---
title: "prevelance"
output: word_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r pfs_mas, echo=FALSE, results='hide', warning=FALSE, include=FALSE}
library(readr)
library(ggplot2)
library(meta)
library(forestplot)
library(stringr)
library(readxl)
library(tidyverse)
library(rstatix)

```


```{r, echo=FALSE, message = FALSE, warning=FALSE, include=FALSE}
#for prevalance table 
neurobypass <- read_excel("cleanforcoding.xlsx")

#total overall
Totalcount <-nrow(neurobypass)

Totalpreceededsubset<-subset(neurobypass, preceeded == "1")
Totalambigioussubset<-subset(neurobypass, Ambigious == "1")
Totalbypasssubset<-subset(neurobypass, Truebypass == "1")
  
Totalpreceededcount<-nrow(Totalpreceededsubset)
Totalambigiouscount<-nrow(Totalambigioussubset)
Totalbypasscount<-nrow(Totalbypasssubset)

Totalpreceededpercent <- (divide_by(Totalpreceededcount,Totalcount))*100
Totalambigiouspercent <- (divide_by(Totalambigiouscount,Totalcount))*100
Totalbypasspercent <- (divide_by(Totalbypasscount,Totalcount))*100

#subsets
ADsubset <- subset(neurobypass, indication == "AD")
PDsubset <- subset(neurobypass, indication == "PD")
ALSsubset <- subset(neurobypass, indication == "ALS")
HDsubset <- subset(neurobypass, indication == "Huntingtons")
MSsubset <- subset(neurobypass, indication == "MS")
Migrainesubset <- subset(neurobypass, indication == "Migrane")
Headachesubset <- subset(neurobypass, indication == "Headache")
Epilepsysubset <- subset(neurobypass, indication == "Epilepsy")
TBIsubset <- subset(neurobypass, indication == "TBI")
Strokesubset <- subset(neurobypass, indication == "Stroke")

#totalcount
ADcount <- nrow(ADsubset)
PDcount <- nrow(PDsubset)
ALScount <- nrow(ALSsubset)
HDcount <- nrow(HDsubset)
MScount <- nrow(MSsubset)
Migrainecount <- nrow(Migrainesubset)
Headachecount <- nrow(Headachesubset)
Epilepsycount <- nrow(Epilepsysubset)
TBIcount <- nrow(TBIsubset)
Strokecount <- nrow(Strokesubset)

#precededsubset
ADpreceeded <- subset(ADsubset, preceeded == "1")
PDpreceeded<- subset(PDsubset, preceeded == "1")
ALSpreceeded <- subset(ALSsubset, preceeded == "1")
HDpreceeded <- subset(HDsubset, preceeded == "1")
MSpreceeded <- subset(MSsubset, preceeded == "1")
Migrainepreceeded <- subset(Migrainesubset, preceeded == "1")
Headachepreceeded <- subset(Headachesubset, preceeded == "1")
Epilepsypreceeded <- subset(Epilepsysubset, preceeded == "1")
TBIpreceeded <- subset(TBIsubset, preceeded == "1")
Strokepreceeded <- subset(Strokesubset, preceeded == "1")

#precededcount
ADpreceededcount <- nrow(ADpreceeded)
PDpreceededcount <- nrow(PDpreceeded)
ALSpreceededcount <- nrow(ALSpreceeded)
HDpreceededcount <- nrow(HDpreceeded)
MSpreceededcount <- nrow(MSpreceeded)
Migrainepreceededcount <- nrow(Migrainepreceeded)
Headachepreceededcount <- nrow(Headachepreceeded)
Epilepsypreceededcount <- nrow(Epilepsypreceeded)
TBIpreceededcount <- nrow(TBIpreceeded)
Strokepreceededcount <- nrow(Strokepreceeded)

#precededpercent
ADpcdpercent <- (divide_by(ADpreceededcount,ADcount))*100
PDpcdpercent <- (divide_by(PDpreceededcount,PDcount))*100
ALSpcdpercent <- (divide_by(ALSpreceededcount,ALScount))*100
HDpcdpercent <- (divide_by(HDpreceededcount,HDcount))*100
MSpcdpercent <- (divide_by(MSpreceededcount,MScount))*100
Migrainepcdpercent <-(divide_by(Migrainepreceededcount,Migrainecount))*100
Headachepcdpercent <- (divide_by(Headachepreceededcount,Headachecount))*100
Epilepsypcdpercent <- (divide_by(Epilepsypreceededcount,Epilepsycount))*100
TBIpcdpercent <- (divide_by(TBIpreceededcount,TBIcount))*100
Strokepcdpercent <- (divide_by(Strokepreceededcount,Strokecount))*100
#bypass is opposite percent

#ambig
ADpreceededambi <- subset(ADsubset, Ambigious == "1")
PDpreceededambi<- subset(PDsubset, Ambigious == "1")
ALSpreceededambi <- subset(ALSsubset, Ambigious == "1")
HDpreceededambi <- subset(HDsubset, Ambigious == "1")
MSpreceededambi <- subset(MSsubset, Ambigious == "1")
Migrainepreceededambi <- subset(Migrainesubset, Ambigious == "1")
Headachepreceededambi <- subset(Headachesubset, Ambigious == "1")
Epilepsypreceededambi <- subset(Epilepsysubset, Ambigious == "1")
TBIpreceededambi <- subset(TBIsubset, Ambigious == "1")
Strokepreceededambi <- subset(Strokesubset, Ambigious == "1")

#precededambicount
ADpreceededcountambi <- nrow(ADpreceededambi)
PDpreceededcountambi <- nrow(PDpreceededambi)
ALSpreceededcountambi <- nrow(ALSpreceededambi)
HDpreceededcountambi <- nrow(HDpreceededambi)
MSpreceededcountambi <- nrow(MSpreceededambi)
Migrainepreceededcountambi <- nrow(Migrainepreceededambi)
Headachepreceededcountambi <- nrow(Headachepreceededambi)
Epilepsypreceededcountambi <- nrow(Epilepsypreceededambi)
TBIpreceededcountambi <- nrow(TBIpreceededambi)
Strokepreceededcountambi <- nrow(Strokepreceededambi)

#precededambipercent
ADpcdpercentambi <- (divide_by(ADpreceededcountambi,ADcount))*100
PDpcdpercentambi <- (divide_by(PDpreceededcountambi,PDcount))*100
ALSpcdpercentambi <- (divide_by(ALSpreceededcountambi,ALScount))*100
HDpcdpercentambi <- (divide_by(HDpreceededcountambi,HDcount))*100
MSpcdpercentambi <- (divide_by(MSpreceededcountambi,MScount))*100
Migrainepcdpercentambi <-(divide_by(Migrainepreceededcountambi,Migrainecount))*100
Headachepcdpercentambi <- (divide_by(Headachepreceededcountambi,Headachecount))*100
Epilepsypcdpercentambi <- (divide_by(Epilepsypreceededcountambi,Epilepsycount))*100
TBIpcdpercentambi <- (divide_by(TBIpreceededcountambi,TBIcount))*100
Strokepcdpercentambi <- (divide_by(Strokepreceededcountambi,Strokecount))*100

#Bypasstruenumber 
  
ADtruebpnumber <- (ADcount-(ADpreceededcountambi+ADpreceededcount))
PDtruebpnumber <- (PDcount-(PDpreceededcountambi+PDpreceededcount))
ALStruebpnumber <- (ALScount-(ALSpreceededcountambi+ALSpreceededcount))
HDtruebpnumber <- (HDcount-(HDpreceededcountambi+HDpreceededcount))
MStruebpnumber <- (MScount-(MSpreceededcountambi+MSpreceededcount))
Migrainetruebpnumber <- (Migrainecount-(Migrainepreceededcountambi+Migrainepreceededcount))
Headachetruebpnumber <- (Headachecount-(Headachepreceededcountambi+Headachepreceededcount))
Epilepsytruebpnumber <- (Epilepsycount-(Epilepsypreceededcountambi+Epilepsypreceededcount))
TBItruebpnumber <- (TBIcount-(TBIpreceededcountambi+TBIpreceededcount))
Stroketruebpnumber <- (Strokecount-(Strokepreceededcountambi+Strokepreceededcount))

#Bypasstruepercent 

ADtruebppercent <- 100-ADpcdpercentambi
PDtruebppercent <- 100-PDpcdpercentambi
ALStruebppercent <- 100-ALSpcdpercentambi
HDtruebppercent <- 100-HDpcdpercentambi
MStruebpdpercent <- 100-MSpcdpercentambi
Migrainetruebppercent <- 100-Migrainepcdpercentambi
Headachetruebppercent <- 100-Headachepcdpercentambi
Epilepsytruebppercent <- 100-Epilepsypcdpercentambi
TBItruebppercent <- 100-TBIpcdpercentambi
Stroketruebppercent <- 100-Strokepcdpercentambi

Indicationvector1<-c("All indications", "Alzheimer'ss disease","Parkinson's disease","Amyotrophic lateral sclerosis","Huntington's disease","Multiple sclerosis","Migraine","Headache","Epilepsy","TBI","Stroke")

NumberofTrials<- c(Totalcount, ADcount, PDcount, ALScount, HDcount, MScount, Migrainecount, Headachecount, Epilepsycount, TBIcount, Strokecount)

PreceededNumber<- c(Totalpreceededcount,ADpreceededcount,PDpreceededcount,ALSpreceededcount,HDpreceededcount,MSpreceededcount,Migrainepreceededcount,Headachepreceededcount,Epilepsypreceededcount,TBIpreceededcount, Strokepreceededcount)
PreceededRate<- c(Totalpreceededpercent, ADpcdpercent, PDpcdpercent, ALSpcdpercent, HDpcdpercent, MSpcdpercent, Migrainepcdpercent, Headachepcdpercent, Epilepsypcdpercent,TBIpcdpercent, Strokepcdpercent)

PreceededambiNumber <- c(Totalambigiouscount,ADpreceededcountambi,PDpreceededcountambi,ALSpreceededcountambi,HDpreceededcountambi,MSpreceededcountambi,Migrainepreceededcountambi,Headachepreceededcountambi,Epilepsypreceededcountambi,TBIpreceededcountambi,Strokepreceededcountambi)
PreceededambiRate <- c(Totalambigiouspercent,ADpcdpercentambi,PDpcdpercentambi,ALSpcdpercentambi,HDpcdpercentambi,MSpcdpercentambi,Migrainepcdpercentambi,Headachepcdpercentambi,Epilepsypcdpercentambi,TBIpcdpercentambi,Strokepcdpercentambi)

Bypasstruenumber <- c(Totalbypasscount,ADtruebpnumber, PDtruebpnumber, ALStruebpnumber, HDtruebpnumber, MStruebpnumber, Migrainetruebpnumber, Headachetruebpnumber, Epilepsytruebpnumber, TBItruebpnumber, Stroketruebpnumber)
Bypasstruepercent <- c(Totalbypasspercent, ADtruebppercent, PDtruebppercent, ALStruebppercent, HDtruebppercent, MStruebpdpercent,Migrainetruebppercent, Headachetruebppercent, Epilepsytruebppercent, TBItruebppercent, Stroketruebppercent)

prevelance <- data.frame(Indication=rep(Indicationvector1),
                 Number_of_P3_Trials=rep(NumberofTrials),
                 PreceededNumber=rep(PreceededNumber),
                 PreceededRate=rep(PreceededRate),
                 AmbigiousNumber=rep(PreceededambiNumber),
                 AmbigiousRate=rep(PreceededambiRate),
                 Bypasstruenumber=rep(Bypasstruenumber),
                 Bypasstruepercent=rep(Bypasstruepercent)
                 )

#view head of data 
print(prevelance)


```

```{r, echo=FALSE, message = FALSE, warning=FALSE, include=FALSE}
#for association table
#overall

OverallIndustrysubset <- subset(neurobypass, pharmafunding == "pharma")
OverallApprovedsubset <- subset(neurobypass, approval == "1")
OverallSymptomsubset<- subset(neurobypass, Symptom_focus == "Not_symptom_focus")
OverallSeveritysubset<- subset(neurobypass, severity == "1")

OverallIndustrynumber <- nrow(OverallIndustrysubset)
OverallApprovednumber <- nrow(OverallApprovedsubset)
OverallSymptomnumber<- nrow(OverallSymptomsubset)
OverallSeveritynumber<- nrow(OverallSeveritysubset)

OverallIndustrypercent <- (divide_by(OverallIndustrynumber,Totalcount))*100
OverallApprovedpercent <- (divide_by(OverallApprovednumber,Totalcount))*100
OverallSymptompercent<- (divide_by(OverallSymptomnumber,Totalcount))*100
OverallSeveritypercent<- (divide_by(OverallSeveritynumber,Totalcount))*100
#proceeded
Procsubset<-subset(neurobypass,preceeded=="1")
Procnumber<-nrow(Procsubset)

ProcIndustrysubset <- subset(Procsubset, pharmafunding == "pharma")
ProcApprovedsubset <- subset(Procsubset, approval == "1")
ProcSymptomsubset<- subset(Procsubset, Symptom_focus == "Not_symptom_focus")
ProcSeveritysubset<- subset(Procsubset, severity == "1")

ProcIndustrynumber <- nrow(ProcIndustrysubset)
ProcApprovednumber <- nrow(ProcApprovedsubset)
ProcSymptomnumber<- nrow(ProcSymptomsubset)
ProcSeveritynumber<- nrow(ProcSeveritysubset)

ProcIndustrypercent <- (divide_by(ProcIndustrynumber,Procnumber))*100
ProcApprovedpercent <- (divide_by(ProcApprovednumber,Procnumber))*100
ProcSymptompercent<- (divide_by(ProcSymptomnumber,Procnumber))*100
ProcSeveritypercent<- (divide_by(ProcSeveritynumber,Procnumber))*100

BroadBypass <-subset(neurobypass,preceeded=="0")
BroadBypassnumber <-nrow(BroadBypass)

BroadBypassIndustrysubset <- subset(BroadBypass, pharmafunding == "pharma")
BroadBypassApprovedsubset <- subset(BroadBypass, approval == "1")
BroadBypassSymptomsubset<- subset(BroadBypass, Symptom_focus = "Not_symptom_focus")
BroadBypassSeveritysubset<- subset(BroadBypass, severity == "1")

BroadBypassIndustrynumber <- nrow(BroadBypassIndustrysubset)
BroadBypassApprovednumber <- nrow(BroadBypassApprovedsubset)
BroadBypassSymptomnumber<- nrow(BroadBypassSymptomsubset)
BroadBypassSeveritynumber<- nrow(BroadBypassSeveritysubset)

BroadBypassIndustrypercent <- (divide_by(BypassIndustrynumber,BroadBypassnumber))*100
BroadBypassApprovedpercent <- (divide_by(BypassApprovednumber,BroadBypassnumber))*100
BroadBypassSymptompercent<- (divide_by(BypassSymptomnumber,BroadBypassnumber))*100
BroadBypassSeveritypercent<- (divide_by(BypassSeveritynumber,BroadBypassnumber))*100

Names<-c("Pharma funded","Approved","Disease modifying intervention","Severe disease")

Overallsecondaries<-c(OverallIndustrypercent,OverallApprovedpercent,OverallSymptompercent,OverallSeveritypercent)
Proceededsecondaries<-c(ProcIndustrypercent,ProcApprovedpercent,ProcSymptompercent,ProcSeveritypercent)
Broadbypasssecondaries<-c(BroadBypassIndustrypercent,BroadBypassApprovedpercent,BroadBypassSymptompercent,BroadBypassSeveritypercent)

secondariestable <- data.frame(Secondary=rep(Names),
                 All_Trials=rep(Overallsecondaries),
                 Percent_of_Trials_Proceeded_by_P2_inthis_category=rep(Proceededsecondaries),
                 Percent_of_Trials_that_Bypassed_P2_inthis_category=rep(Broadbypasssecondaries)
                 )

print(secondariestable)
```
 

```{r, echo=FALSE, message = FALSE, warning=FALSE, include=FALSE}
neurobypass <- read_excel("cleanforcoding.xlsx")
#for positivity

#AllP2STATUS
Overallpossubset <- subset(neurobypass, positivityofP3 == "Positive")
ADpossubset <- subset(ADsubset, positivityofP3 == "Positive")
PDpossubset <- subset(PDsubset, positivityofP3 == "Positive")
ALSpossubset <- subset(ALSsubset, positivityofP3 == "Positive")
HDpossubset <- subset(HDsubset, positivityofP3 == "Positive")
MSpossubset <- subset(MSsubset, positivityofP3 == "Positive")
Migrainepossubset <- subset(Migrainesubset, positivityofP3 == "Positive")
Headachepossubset <- subset(Headachesubset, positivityofP3 == "Positive")
Epilepsypossubset <- subset(Epilepsysubset, positivityofP3 == "Positive")
TBIpossubset <- subset(TBIsubset, positivityofP3 == "Positive")
Strokepossubset <- subset(Strokesubset, positivityofP3 == "Positive")

#poscount
Overallposcount <- nrow(Overallpossubset)
ADposcount <- nrow(ADpossubset)
PDposcount <- nrow(PDpossubset)
ALSposcount <- nrow(ALSpossubset)
HDposcount <- nrow(HDpossubset)
MSposcount <- nrow(MSpossubset)
Migraineposcount <- nrow(Migrainepossubset)
Headacheposcount <- nrow(Headachepossubset)
Epilepsyposcount <- nrow(Epilepsypossubset)
TBIposcount <- nrow(TBIpossubset)
Strokeposcount <- nrow(Strokepossubset)

#pospercent
Overallpospercent <- (divide_by(Overallposcount,Totalcount))*100
ADpospercent <- (divide_by(ADposcount,ADcount))*100
PDpospercent <- (divide_by(PDposcount,PDcount))*100
ALSpospercent <- (divide_by(ALSposcount,ALScount))*100
HDpospercent <- (divide_by(HDposcount,HDcount))*100
MSpospercent <- (divide_by(MSposcount,MScount))*100
Migrainepospercent <-(divide_by(Migraineposcount,Migrainecount))*100
Headachepospercent <- (divide_by(Headacheposcount,Headachecount))*100
Epilepsypospercent <- (divide_by(Epilepsyposcount,Epilepsycount))*100
TBIpospercent <- (divide_by(TBIposcount,TBIcount))*100
Strokepospercent <- (divide_by(Strokeposcount,Strokecount))*100

#PROCEEDED
#proceededpos
Overallpreceed <- subset(neurobypass, preceeded == "1")
ADpreceed <- subset(ADsubset, preceeded == "1")
PDpreceed<- subset(PDsubset, preceeded == "1")
ALSpreceed <- subset(ALSsubset, preceeded == "1")
HDpreceed <- subset(HDsubset, preceeded == "1")
MSpreceed <- subset(MSsubset, preceeded == "1")
Migrainepreceed <- subset(Migrainesubset, preceeded == "1")
Headachepreceed <- subset(Headachesubset, preceeded == "1")
Epilepsypreceed <- subset(Epilepsysubset, preceeded == "1")
TBIpreceed <- subset(TBIsubset, preceeded == "1")
Strokepreceed <- subset(Strokesubset, preceeded == "1")

Overallpreceedcount <- nrow(Overallpreceed)
ADpreceedcount <- nrow(ADpreceed)
PDpreceedcount <- nrow(PDpreceed)
ALSpreceedcount <- nrow(ALSpreceed)
HDpreceedcount <- nrow(HDpreceed)
MSpreceedcount <- nrow(MSpreceed)
Migrainepreceedcount <- nrow(Migrainepreceed)
Headachepreceedcount <- nrow(Headachepreceed)
Epilepsypreceedcount <- nrow(Epilepsypreceed)
TBIpreceedcount <- nrow(TBIpreceed)
Strokepreceedcount <- nrow(Strokepreceed)

Overallprecedpos <- subset(Overallpreceed, positivityofP3 == "Positive")
ADprecedpos <- subset(ADpreceed, positivityofP3 == "Positive")
PDprecedpos<- subset(PDpreceed, positivityofP3 == "Positive")
ALSprecedpos <- subset(ALSpreceed, positivityofP3 == "Positive")
HDprecedpos <- subset(HDpreceed, positivityofP3 == "Positive")
MSprecedpos <- subset(MSpreceed, positivityofP3 == "Positive")
Migraineprecedpos <- subset(Migrainepreceed, positivityofP3 == "Positive")
Headacheprecedpos <- subset(Headachepreceed, positivityofP3 == "Positive")
Epilepsyprecedpos <- subset(Epilepsypreceed, positivityofP3 == "Positive")
TBIprecedpos <- subset(TBIpreceed, positivityofP3 == "Positive")
Strokeprecedpos <- subset(Strokepreceed, positivityofP3 == "Positive")

Overallprecposnumber <-nrow(Overallprecedpos)
ADprecposnumber <- nrow(ADprecedpos)
PDprecposnumber <- nrow(PDprecedpos)
ALSprecposnumber  <- nrow(ALSprecedpos)
HDprecposnumber  <- nrow(HDprecedpos)
MSprecposnumber  <- nrow(MSprecedpos)
Migraineprecposnumber  <- nrow(Migraineprecedpos)
Headacheprecposnumber  <- nrow(Headacheprecedpos)
Epilepsyprecposnumber  <- nrow(Epilepsyprecedpos)
TBIprecposnumber  <- nrow(TBIprecedpos)
Strokeprecposnumber  <- nrow(Strokeprecedpos)

Overallprecedpospercent <- (divide_by(Overallprecposnumber,Overallpreceedcount))*100
ADprecedpospercent <- (divide_by(ADprecposnumber,ADpreceedcount))*100
PDprecedpospercent <- (divide_by(PDprecposnumber,PDpreceedcount))*100
ALSprecedpospercent  <- (divide_by(ALSprecposnumber,ALSpreceedcount))*100
HDprecedpospercent <- (divide_by(HDprecposnumber,HDpreceedcount))*100
MSprecedpospercent <- (divide_by(MSprecposnumber,MSpreceedcount))*100
Migraineprecedpospercent <- (divide_by(Migraineprecposnumber,Migrainepreceedcount))*100
Headacheprecedpospercent <- (divide_by(Headacheprecposnumber,Headachepreceedcount))*100
Epilepsyprecedpospercent <- (divide_by(Epilepsyprecposnumber,Epilepsypreceedcount))*100
TBIprecedpospercent <- (divide_by(TBIprecposnumber,TBIpreceedcount))*100
Strokeprecedposnumber  <- (divide_by(Strokeprecposnumber,Strokepreceedcount))*100

#BYPASS
Overallbypassandambi <- subset(neurobypass, preceeded == "0")
ADbypassandambi <- subset(ADsubset, preceeded == "0")
PDbypassandambi<- subset(PDsubset, preceeded == "0")
ALSbypassandambi <- subset(ALSsubset, preceeded == "0")
HDbypassandambi <- subset(HDsubset, preceeded == "0")
MSbypassandambi <- subset(MSsubset, preceeded == "0")
Migrainebypassandambi <- subset(Migrainesubset, preceeded == "0")
Headachebypassandambi <- subset(Headachesubset, preceeded == "0")
Epilepsybypassandambi <- subset(Epilepsysubset, preceeded == "0")
TBIbypassandambi <- subset(TBIsubset, preceeded == "0")
Strokebypassandambi <- subset(Strokesubset, preceeded == "0")

Overallbypassandambicount<- nrow(Overallbypassandambi)
ADbypassandambicount <- nrow(ADbypassandambi)
PDbypassandambicount <- nrow(PDbypassandambi)
ALSbypassandambicount <- nrow(ALSbypassandambi)
HDbypassandambicount <- nrow(HDbypassandambi)
MSbypassandambicount <- nrow(MSbypassandambi)
Migrainebypassandambicount <- nrow(Migrainebypassandambi)
Headachebypassandambicount <- nrow(Headachebypassandambi)
Epilepsybypassandambicount <- nrow(Epilepsybypassandambi)
TBIbypassandambicount <- nrow(TBIbypassandambi)
Strokebypassandambicount <- nrow(Strokebypassandambi)

Overallbypasspos <- subset(Overallbypassandambi, positivityofP3 == "Positive")
ADbypasspos <- subset(ADbypassandambi, positivityofP3 == "Positive")
PDbypasspos<- subset(PDbypassandambi, positivityofP3 == "Positive")
ALSbypasspos <- subset(ALSbypassandambi, positivityofP3 == "Positive")
HDbypasspos <- subset(HDbypassandambi, positivityofP3 == "Positive")
MSbypasspos <- subset(MSbypassandambi, positivityofP3 == "Positive")
Migrainebypasspos <- subset(Migrainebypassandambi, positivityofP3 == "Positive")
Headachebypasspos <- subset(Headachebypassandambi, positivityofP3 == "Positive")
Epilepsybypasspos <- subset(Epilepsybypassandambi, positivityofP3 == "Positive")
TBIbypasspos <- subset(TBIbypassandambi, positivityofP3 == "Positive")
Strokebypasspos <- subset(Strokebypassandambi, positivityofP3 == "Positive")

Overallbypassposnumber <- nrow(Overallbypasspos)
ADbypassposnumber <- nrow(ADbypasspos)
PDbypassposnumber <- nrow(PDbypasspos)
ALSbypassposnumber  <- nrow(ALSbypasspos)
HDbypassposnumber  <- nrow(HDbypasspos)
MSbypassposnumber  <- nrow(MSbypasspos)
Migrainebypassposnumber  <- nrow(Migrainebypasspos)
Headachebypassposnumber  <- nrow(Headachebypasspos)
Epilepsybypassposnumber  <- nrow(Epilepsybypasspos)
TBIbypassposnumber  <- nrow(TBIbypasspos)
Strokebypassposnumber  <- nrow(Strokebypasspos)

Overallbypasspospercent <-(divide_by(Overallbypassposnumber,Overallbypassandambicount))*100
ADbypasspospercent <- (divide_by(ADbypassposnumber,ADbypassandambicount))*100
PDbypasspospercent <- (divide_by(PDbypassposnumber,PDbypassandambicount))*100
ALSbypasspospercent  <- (divide_by(ALSbypassposnumber,ALSbypassandambicount))*100
HDbypasspospercent <- (divide_by(HDbypassposnumber,HDbypassandambicount))*100
MSbypasspospercent <- (divide_by(MSbypassposnumber,MSbypassandambicount))*100
Migrainebypasspospercent <- (divide_by(Migrainebypassposnumber,Migrainebypassandambicount))*100
Headachebypasspospercent <- (divide_by(Headachebypassposnumber,Headachebypassandambicount))*100
Epilepsybypasspospercent <- (divide_by(Epilepsybypassposnumber,Epilepsybypassandambicount))*100
TBIbypasspospercent <- (divide_by(TBIbypassposnumber,TBIbypassandambicount))*100
Strokebypassposnumber  <- (divide_by(Strokebypassposnumber,Strokebypassandambicount))*100

#TERMINATION
#all indications term
Overalltermsubset <- subset(neurobypass, terminationcode == "1")
ADtermsubset <- subset(ADsubset, terminationcode == "1")
PDtermsubset <- subset(PDsubset,terminationcode == "1")
ALStermsubset <- subset(ALSsubset, terminationcode == "1")
HDtermsubset <- subset(HDsubset, terminationcode == "1")
MStermsubset <- subset(MSsubset, terminationcode == "1")
Migrainetermsubset <- subset(Migrainesubset, terminationcode == "1")
Headachetermsubset <- subset(Headachesubset, terminationcode == "1")
Epilepsytermsubset <- subset(Epilepsysubset, terminationcode == "1")
TBItermsubset <- subset(TBIsubset, terminationcode == "1")
Stroketermsubset <- subset(Strokesubset, terminationcode == "1")

#poscount
Overalltermcount <- nrow(Overalltermsubset)
ADtermcount <- nrow(ADtermsubset)
PDtermcount <- nrow(PDtermsubset)
ALStermcount <- nrow(ALStermsubset)
HDtermcount <- nrow(HDtermsubset)
MStermcount <- nrow(MStermsubset)
Migrainetermcount <- nrow(Migrainetermsubset)
Headachetermcount <- nrow(Headachetermsubset)
Epilepsytermcount <- nrow(Epilepsytermsubset)
TBItermcount <- nrow(TBItermsubset)
Stroketermcount <- nrow(Stroketermsubset)

#pospercent
Overalltermpercent <- (divide_by(Overalltermcount,Totalcount))*100
ADtermpercent <- (divide_by(ADtermcount,ADcount))*100
PDtermpercent <- (divide_by(PDtermcount,PDcount))*100
ALStermpercent <- (divide_by(ALStermcount,ALScount))*100
HDtermpercent <- (divide_by(HDtermcount,HDcount))*100
MStermpercent <- (divide_by(MStermcount,MScount))*100
Migrainetermpercent <-(divide_by(Migrainetermcount,Migrainecount))*100
Headachetermpercent <- (divide_by(Headachetermcount,Headachecount))*100
Epilepsytermpercent <- (divide_by(Epilepsytermcount,Epilepsycount))*100
TBItermpercent <- (divide_by(TBItermcount,TBIcount))*100
Stroketermpercent <- (divide_by(Stroketermcount,Strokecount))*100

#preceded term
Overallpreceedterm <-subset(Overallpreceed, terminationcode == "1")
ADprecedterm <- subset(ADpreceed, terminationcode == "1")
PDprecedterm<- subset(PDpreceed, terminationcode == "1")
ALSprecedterm <- subset(ALSpreceed, terminationcode == "1")
HDprecedterm <- subset(HDpreceed, terminationcode == "1")
MSprecedterm <- subset(MSpreceed, terminationcode == "1")
Migraineprecedterm <- subset(Migrainepreceed, terminationcode == "1")
Headacheprecedterm <- subset(Headachepreceed, terminationcode == "1")
Epilepsyprecedterm <- subset(Epilepsypreceed, terminationcode == "1")
TBIprecedterm <- subset(TBIpreceed, terminationcode == "1")
Strokeprecedterm <- subset(Strokepreceed, terminationcode == "1")

Overallprectermnumber <- nrow(Overallpreceedterm)
ADprectermnumber <- nrow(ADprecedterm)
PDprectermnumber <- nrow(PDprecedterm)
ALSprectermnumber  <- nrow(ALSprecedterm)
HDprectermnumber  <- nrow(HDprecedterm)
MSprectermnumber  <- nrow(MSprecedterm)
Migraineprectermnumber  <- nrow(Migraineprecedterm)
Headacheprectermnumber  <- nrow(Headacheprecedterm)
Epilepsyprectermnumber  <- nrow(Epilepsyprecedterm)
TBIprectermnumber  <- nrow(TBIprecedterm)
Strokeprectermnumber  <- nrow(Strokeprecedterm)

Overallprecedtermpercent <- (divide_by(Overallprectermnumber,Overallpreceedcount))*100
ADprecedtermpercent <- (divide_by(ADprectermnumber,ADpreceedcount))*100
PDprecedtermpercent <- (divide_by(PDprectermnumber,PDpreceedcount))*100
ALSprecedtermpercent  <- (divide_by(ALSprectermnumber,ALSpreceedcount))*100
HDprecedtermpercent <- (divide_by(HDprectermnumber,HDpreceedcount))*100
MSprecedtermpercent <- (divide_by(MSprectermnumber,MSpreceedcount))*100
Migraineprecedtermpercent <- (divide_by(Migraineprectermnumber,Migrainepreceedcount))*100
Headacheprecedtermpercent <- (divide_by(Headacheprectermnumber,Headachepreceedcount))*100
Epilepsyprecedtermpercent <- (divide_by(Epilepsyprectermnumber,Epilepsypreceedcount))*100
TBIprecedtermpercent <- (divide_by(TBIprectermnumber,TBIpreceedcount))*100
Strokeprecedtermpercent  <- (divide_by(Strokeprectermnumber,Strokepreceedcount))*100

#bypassterm
Overallbypassterm<-subset(Overallbypassandambi, terminationcode == "1")
ADbypassterm <- subset(ADbypassandambi, terminationcode == "1")
PDbypassterm<- subset(PDbypassandambi, terminationcode == "1")
ALSbypassterm <- subset(ALSbypassandambi, terminationcode == "1")
HDbypassterm <- subset(HDbypassandambi, terminationcode == "1")
MSbypassterm <- subset(MSbypassandambi, terminationcode == "1")
Migrainebypassterm <- subset(Migrainebypassandambi, terminationcode == "1")
Headachebypassterm <- subset(Headachebypassandambi, terminationcode == "1")
Epilepsybypassterm <- subset(Epilepsybypassandambi, terminationcode == "1")
TBIbypassterm <- subset(TBIbypassandambi, terminationcode == "1")
Strokebypassterm <- subset(Strokebypassandambi, terminationcode == "1")

Overallbypasstermnumber <- nrow(Overallbypassterm)
ADbypasstermnumber <- nrow(ADbypassterm)
PDbypasstermnumber <- nrow(PDbypassterm)
ALSbypasstermnumber  <- nrow(ALSbypassterm)
HDbypasstermnumber  <- nrow(HDbypassterm)
MSbypasstermnumber  <- nrow(MSbypassterm)
Migrainebypasstermnumber  <- nrow(Migrainebypassterm)
Headachebypasstermnumber  <- nrow(Headachebypassterm)
Epilepsybypasstermnumber  <- nrow(Epilepsybypassterm)
TBIbypasstermnumber  <- nrow(TBIbypassterm)
Strokebypasstermnumber  <- nrow(Strokebypassterm)

Overallbypasstermpercent <- (divide_by(Overallbypasstermnumber,Overallbypassandambicount))*100
ADbypasstermpercent <- (divide_by(ADbypasstermnumber,ADbypassandambicount))*100
PDbypasstermpercent <- (divide_by(PDbypasstermnumber,PDbypassandambicount))*100
ALSbypasstermpercent  <- (divide_by(ALSbypasstermnumber,ALSbypassandambicount))*100
HDbypasstermpercent <- (divide_by(HDbypasstermnumber,HDbypassandambicount))*100
MSbypasstermpercent <- (divide_by(MSbypasstermnumber,MSbypassandambicount))*100
Migrainebypasstermpercent <- (divide_by(Migrainebypasstermnumber,Migrainebypassandambicount))*100
Headachebypasstermpercent <- (divide_by(Headachebypasstermnumber,Headachebypassandambicount))*100
Epilepsybypasstermpercent <- (divide_by(Epilepsybypasstermnumber,Epilepsybypassandambicount))*100
TBIbypasstermpercent <- (divide_by(TBIbypasstermnumber,TBIbypassandambicount))*100
Strokebypasstermnumber  <- (divide_by(Strokebypasstermnumber,Strokebypassandambicount))*100

Indicationvector1<-c("All Indications","Alzheimer's disease","Parkinson's disease","Amyotrophic lateral sclerosis","Huntington's disease","Multiple sclerosis","Migraine","Headache","Epilepsy","TBI","Stroke")

PositivityRate<- c(Overallpospercent,ADpospercent,PDpospercent,ALSpospercent,HDpospercent,MSpospercent,Migrainepospercent,Headachepospercent,Epilepsypospercent,TBIpospercent,Strokepospercent)

proceedthatwerepospercent <- c(Overallprecedpospercent, ADprecedpospercent, PDprecedpospercent, ALSprecedpospercent, HDprecedpospercent, MSprecedpospercent,Migraineprecedpospercent,Headacheprecedpospercent,Epilepsyprecedpospercent,TBIprecedpospercent,Strokeprecedposnumber)

bypassedthatwerepospercent<- c(Overallbypasspospercent,ADbypasspospercent,PDbypasspospercent, ALSbypasspospercent, HDbypasspospercent,MSbypasspospercent,Migrainebypasspospercent,Headachebypasspospercent,Epilepsybypasspospercent, TBIbypasspospercent, Strokebypassposnumber)

TerminationRate<-c(Overalltermpercent,ADtermpercent,PDtermpercent,ALStermpercent,HDtermpercent,MStermpercent,Migrainetermpercent,Headachetermpercent,Epilepsytermpercent,TBItermpercent,Stroketermpercent)

proceedthatweretermpercent <- c(Overallprecedtermpercent, ADprecedtermpercent,PDprecedtermpercent, ALSprecedtermpercent, HDprecedtermpercent, MSprecedtermpercent, Migraineprecedtermpercent, Headacheprecedtermpercent, Epilepsyprecedtermpercent, TBIprecedtermpercent, Strokeprecedtermpercent)

bypassedthatweretermpercent<- c(Overallbypasstermpercent,ADbypasstermpercent,PDbypasstermpercent, ALSbypasstermpercent, HDbypasstermpercent,MSbypasstermpercent,Migrainebypasstermpercent,Headachebypasstermpercent,Epilepsybypasstermpercent, TBIbypasstermpercent, Strokebypasstermnumber)

positivityandtermtable <- data.frame(Indication=rep(Indicationvector1),
                 Positivity_Rate=rep(PositivityRate),
                 Positivity_Rate_when_proceeded_by_P2=rep(proceedthatwerepospercent),
                 Positivity_Rate_when_bypassed=rep(bypassedthatwerepospercent),
                 Termination_Rate=rep(TerminationRate),
                 Termination_Rate_when_proceeded=rep(proceedthatweretermpercent),
                 Termination_Rate_when_bypassed=rep(bypassedthatweretermpercent)
                 )

print(positivityandtermtable)

```


```{r, echo=FALSE, message = FALSE, warning=FALSE, include=FALSE}
#for SMD&for WdAe
SMDpool <- SMDpool %>%
  mutate(SMD_SE =   ((ABS(LOG(upperCI))-(LOG(lowerCI)))/(ABS(qnorm((1-0.95)/2))*2)))

#seperate into indications-only these are included for now--check again when new data is added
#Alzheimer’s disease, Parkinson’s disease, Migraine

ADsubset <- subset(neurobypass, indication == "AD")
PDsubset <- subset(neurobypass, indication == "PD")
Migrainesubset <- subset(neurobypass, indication == "Migrane")

ADSMDpool <- subset(ADsubset, Is_there_a_SMD == "1")
PDSMDpool <- subset(PDsubset, Is_there_a_SMD == "1")
MigraineSMDpool <- subset(Migrainesubset, Is_there_a_SMD == "1")

      
#do we log it?                                 
ADSMDpooling <- metagen(
  TE=log(Mean_difference),
  seTE=SMD_SE,
  data = ADSMDpool,
  sm = "Mean difference",
  comb.fixed = FALSE,
  comb.random = TRUE,
  subgroup = preceeded,
  random = T,
  fixed = F,
  tau.common = F,
  method.tau = "SJ", # # "DL", "PM", "REML", "ML", "HS", "SJ", "HE", or "EB"
  adhoc.hakn = "se",
)
summary(ADSMDpooling)

PDSMDpooling <- metagen(
  TE=log(Mean_difference),
  seTE=SMD_SE,
  data = PDSMDpool,
  sm = "Mean difference",
  comb.fixed = FALSE,
  comb.random = TRUE,
  subgroup = preceeded,
  random = T,
  fixed = F,
  tau.common = F,
  method.tau = "SJ", # # "DL", "PM", "REML", "ML", "HS", "SJ", "HE", or "EB"
  adhoc.hakn = "se",
)
summary(PDSMDpooling)

MigraineSMDpooling <- metagen(
  TE=log(Mean_difference),
  seTE=SMD_SE,
  data = MigraineSMDpool,
  sm = "Mean difference",
  comb.fixed = FALSE,
  comb.random = TRUE,
  subgroup = preceeded,
  random = T,
  fixed = F,
  tau.common = F,
  method.tau = "SJ", # # "DL", "PM", "REML", "ML", "HS", "SJ", "HE", or "EB"
  adhoc.hakn = "se",
)
summary(MigraineSMDpooling)

#wdAE
ADwdAE<- subset(ADsubset, Is_there_a_WdueAE == "1")
PDwdAE<- subset(PDsubset, Is_there_a_WdueAE == "1")
MigrainewdAE<- subset(Migrainesubset, Is_there_a_WdueAE == "1")

ADwdAEpooling <- metabin(
  event.e=withdrawals_in_exparm,
  n.e=Nexp_arm,
  event.c=withdrawals_in_contarm,
  n.c=Ncont_arm,
  studlab = nct_id,
  data = ADwdAE, 
  subgroup = preceeded,
  comb.fixed = FALSE,
  fixed = F,
  random = T,
  method.tau = "PM", 
  adhoc.hakn = "se",
)
summary (ADwdAEpooling)

PDwdAEpooling <- metabin(
  event.e=withdrawals_in_exparm,
  n.e=Nexp_arm,
  event.c=withdrawals_in_contarm,
  n.c=Ncont_arm,
  studlab = nct_id,
  data = PDwdAE, 
  subgroup = preceeded,
  comb.fixed = FALSE,
  fixed = F,
  random = T,
  method.tau = "PM", 
  adhoc.hakn = "se",
)
summary (PDwdAEpooling)

MigrainewdAEpooling <- metabin(
  event.e=withdrawals_in_exparm,
  n.e=Nexp_arm,
  event.c=withdrawals_in_contarm,
  n.c=Ncont_arm,
  studlab = nct_id,
  data = MigrainewdAE, 
  subgroup = preceeded,
  comb.fixed = FALSE,
  fixed = F,
  random = T,
  method.tau = "PM", 
  adhoc.hakn = "se",
)
summary (MigrainewdAEpooling)

#forestplots

labels1 <- c("Proceeded", "Bypass")
smdnb <- metabind(ADSMDpooling,PDSMDpooling, MigraineSMDpooling, name = labels1)
saenb <- metabind(ADwdAEpooling,PDwdAEpooling, MigrainewdAEpooling, name = labels1)

pdf("PFSall.pdf",10,8)
forest(smdnb, xlim=c(0.55,1.5), print.subgroup.labels = T,label.left = "<-------------
Favours exp arm",label.right = "--------->
control arm")
dev.off()

pdf("SAEall.pdf",10,8)
forest(saenb, xlim=c(0.75,1.5), print.subgroup.labels = T,label.left = "<---------
Favours exp arm",
       label.right = "------------>
Favours control arm")
dev.off()
```
#write text 
#write variables 
Results Section 

Sample
After applying our inclusion criteria to the downloaded trials, **`r round(Totalcount, 2)`** trials were included in our analysis. Of these trials, **`r round(ADcount, 2)`** trials were in Alzheimer's disease", **`r round(PDcount, 2)`** Parkinson disease,**`r round(ALScount, 2)`** Amyotrophic lateral sclerosis, **`r round(HDcount, 2)`** Huntingtons disease,**`r round(MScount, 2)`** Multiple sclerosis ,**`r round(Migrainecount, 2)`** Migraine,**`r round(Headachecount, 2)`** Headache,**`r round(Epilepsycount, 2)`** Epilepsy,**`r round(TBIcount, 2)`** TBI ,**`r round(Strokecount, 2)`** Stroke. The average sample size was x and x (TABLE 1). 

Prevalence
In our sample, we found that **`r round(Totalpreceededcount, 2)`** were proceeded by a positive P2 trial ,**`r round(Totalambigiouscount, 2)`** were preceded by ambigious evidence, and **`r round(Totalbypasscount, 2)`** lacked any prior evidence that fulfilled our criteria. Overall positivity numbers? Prevalence of bypassing and P3 positivity is broken down into disease areas in Table 1.  Compare indications 

Efficacy and SAEs:


